\chapter{README }
\hypertarget{md__r_e_a_d_m_e}{}\label{md__r_e_a_d_m_e}\index{README@{README}}
\# Easy\+CPP -\/ C++ Made Easy đźš€

!\+[License:\+ MIT]\+(\href{https://img.shields.io/badge/License-MIT-yellow.svg}{\texttt{https:\+/\+/\+img.\+shields.\+io/\+badge/\+\+License-\/\+MIT-\/yellow.\+svg}})

!\+[Standard:\+ C++17]\+(\href{https://img.shields.io/badge/C\%2B\%2B-17-blue.svg}{\texttt{https:\+/\+/\+img.\+shields.\+io/\+badge/\+\+C\%2\+B\%2\+B-\/17-\/blue.\+svg}})

!\+[Status:\+ Active]\+(\href{https://img.shields.io/badge/status-active-brightgreen.svg}{\texttt{https:\+/\+/\+img.\+shields.\+io/\+badge/\+status-\/active-\/brightgreen.\+svg}})

\texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*}124 Python-\/like utility functions for modern C++.\texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*} ~\newline


Stop writing the same boilerplate over and over. {\ttfamily easycpp.\+h} is a \texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*}single-\/header library\texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*} that brings the simplicity of Python to C++ without sacrificing performance.

\#\# âś¨ Why Easy\+CPP?

-\/ \texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*}\+Single Header:\+\texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*} Just drop {\ttfamily easycpp.\+h} into your project and {\ttfamily \#include} it.

-\/ \texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*}\+No Dependencies:\+\texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*} Uses only the C++ Standard Library.

-\/ \texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*}\+Zero Overhead:\+\texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*} {\ttfamily constexpr}, {\ttfamily noexcept}, and {\ttfamily \textbackslash{}\+[\textbackslash{}\+[nodiscard]\+]\+} everywhere.

-\/ \texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*}\+Readable Code:\+\texorpdfstring{$\ast$}{*}\texorpdfstring{$\ast$}{*} Write {\ttfamily \doxylink{_e_a_s_y-_c_p_p_8h_ab8d5c5cd4eb5ba24e8272897a9b1f1a1}{print()}}, {\ttfamily \doxylink{_e_a_s_y-_c_p_p_8h_a9feb8223c82f994e344445c096c57422}{input()}}, {\ttfamily \doxylink{_e_a_s_y-_c_p_p_8h_aa4dda9bff3cd366b4b50dc4bb1922294}{split()}}, {\ttfamily \doxylink{_e_a_s_y-_c_p_p_8h_af2426daf17040a8668703514a3c9f8a8}{trim()}} instead of {\ttfamily std::\+cout \texorpdfstring{$<$}{<}\texorpdfstring{$<$}{<} ... \texorpdfstring{$<$}{<}\texorpdfstring{$<$}{<} std::\+endl;}.

\#\# đźš€ Quick Example

\`{}\`{}\`{}cpp

\#include "{}easycpp.\+h"{}

using namespace std;

int main() \{

\&\+\#x20; /\+/\+ Clean printing

\&\+\#x20; println("{}\+Hello, "{}, "{}\+World!"{}); /\+/\+ Supports multiple args

\&\+\#x20; /\+/\+ Simple input

\&\+\#x20; string name = input\+\_\+str("{}\+What\textquotesingle{}s your name? "{});

\&\+\#x20; int age = input\+\_\+int("{}\+How old are you? "{});

\&\+\#x20; /\+/\+ String utilities

\&\+\#x20; string s = "{}  Hello World  "{};

\&\+\#x20; println(trim(s)); /\+/\+ "{}\+Hello World"{}

\&\+\#x20; vector$<$string$>$ words = split(s); /\+/\+ \{"{}\+Hello"{}, "{}\+World"{}\}

\&\+\#x20; /\+/\+ Vector utilities

\&\+\#x20; vector$<$int$>$ nums = \{1, 2, 3, 4, 5\};

\&\+\#x20; println("{}\+Sum:\+ "{}, sum(nums)); /\+/\+ 15

\&\+\#x20; println("{}\+Avg:\+ "{}, average(nums)); /\+/\+ 3.\+0

\&\+\#x20; /\+/\+ Colored console output

\&\+\#x20; \doxylink{_e_a_s_y-_c_p_p_8h_a0ae17f340b134a9de2a0659aadf1dbe1}{color\+\_\+red()};

\&\+\#x20; println("{}\+This is red!"{});

\&\+\#x20; \doxylink{_e_a_s_y-_c_p_p_8h_afba58386f81a1ece5dee15034d68a4cb}{color\+\_\+reset()};

\&\+\#x20; return 0;

\} 